Scaffolder - Software for Microbial Genome Scaffolding.

### 2011-01-19 text/src/article.tex
Draft outline for results section

% }}}
% {{{ Background
\section*{Background}
 Text for this section.\cite{koon,oreg,khar,zvai,xjon,schn,pond,smith,marg,hunn,advi,koha,mouse}
% }}}
% {{{ Implementation
%%%%%%%%%%%%%%%%%%%%%%
\section*{Implementation}
  Text for this section \ldots
% }}}
% {{{ Results and Discussion

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Results and Discussion %%
%%
\section*{Results and Discussion}
  \subsection*{Results sub-heading}
    \subsubsection*{This is a sub-sub-heading}
      Sub-sub-sub-headings are made with the \textsl{\\subsubsection} command. \pb
      pb at end of lines ensures correct paragraph spacing.\pb
	  Text for this sub-sub-section \ldots
    \subsubsection*{Another sub-sub-sub-heading}
      Text for this sub-sub-section \ldots

  \subsection*{Another results sub-heading}
    Text for this sub-section \ldots

  \subsection*{Yet another results sub-heading}
    Text for this sub-section.  More results \ldots
% }}}
% {{{ Conclusions
%%%%%%%%%%%%%%%%%%%%%%
\section*{Conclusions}
  Text for this section \ldots
% }}}
% {{{ Availability and Requirements
\section*{Availability and Requirements}

>>>>

% }}}
% {{{ Background
\section*{Background}
 Text for this section.\cite{koon,oreg,khar,zvai,xjon,schn,pond,smith,marg,hunn,advi,koha,mouse}
% }}}
% {{{ Implementation
%%%%%%%%%%%%%%%%%%%%%%
\section*{Implementation}
  Text for this section \ldots
% }}}
\section*{Results and Discussion} %{{{1
\subsection*{Scaffolder Description} %{{{2

  * Join contigs together
  * Add inserts
  * Add unknown gap regions
  * Specified in a YAML file format

\subsection*{Scaffold file format} %{{{2

  * Screen shot with example file
  * Illustrate three types of region in the scaffold file
  * Explanation of what each region does
  * Expected output from each region

\subsection*{Command line usage} %{{{2

  * Illustrate running command line to generate output
  * Demonstrate scaffold validate to test inserts overlap

\subsection*{Programmatic usage of API} %{{{2

  * Demonstrate how scaffolder can be manipulated programmatically
  * Examine scaffolder data using a ruby program
  * Example of extending sequence class with a new method \%GC content
  * Create a new class to do something

\subsection*{Installation} %{{{2

  * Install through rubygems
  * Make sure the bin is in the class path

\section*{Conclusions} %{{{1
  Text for this section \ldots
% }}}
% {{{ Availability and Requirements
\section*{Availability and Requirements}
